fractal_data_raw

### 2020-11-11 raw_dwell_times.Rmd
add notes to raw times
suggested additional analyses

# it would be good to try these analyses again with the outliers removed
# can we normalize the data
# put in pictures with tab pills, GIF would be cool
# significant difference between images
# significant difference between sequence position

>>>>

# try these analyses again with the outliers removed
# can we normalize the data
# put in pictures with tab pills, GIF would be cool
# significant difference between images
# significant difference between sequence position
# present each participants most and least viewed
# compare most and least viewed by sequence position
